\bf On semidefinite-representable sets over valuation fields

### 2025-05-15 article/paper_padic_spec.tex
commit by Simone

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{notation}[theorem]{Notation}
\usepackage{booktabs}

\textheight235mm
\textwidth165mm
\voffset-10mm
\hoffset-12.5mm
\parindent0.8cm
\parskip0mm

@@

>>>>

% --------- ALGORITHMS ---------- <<:
\usepackage{algorithm,algorithmic}
%\usepackage[noend]{algpseudocode}      %%% this is for the algorithms
\renewcommand{\algorithmicrequire}{\textbf{Input:}} % require --> input
\renewcommand{\algorithmicensure}{\textbf{Output:}} % ensure --> output
% :>> ALGORITHMS

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{notation}[theorem]{Notation}
\usepackage{booktabs}

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=30mm,
 right=30mm,
 top=30mm,
 bottom=30mm
}

%\textheight235mm
%\textwidth165mm
%\voffset-10mm
%\hoffset-12.5mm
\parindent0.8cm
\parskip0mm

@@

We formalize the algorithm described previously in \Cref{algo_LP}:

\begin{algorithm}
    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE A feasibility type (INFEAS, FEAS) and a solution (if FEAS)
      \vspace{0.1cm}
      \hline
      \vspace{0.1cm}
      \STATE $\mathrm{SOLVELP} (f_i,w_i,o_j)$
      \FOR{epochs = $1$ to $N$}
      \WHILE{$(j\le m)$}
      \STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
      \STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
      \STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
      \STATE compute $e=y-y^2$
      \STATE back propagate $e$ from right to left through layers
      \STATE update $w_i$
      \ENDWHILE
      \ENDFOR
    \end{algorithmic}
\end{algorithm}
